---
title: "Dog Breeds mini dashboard"
author: "Michael K'Ochola"
date: "March 10, 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
breed_traits <- read.csv("breed_traits.csv")
```

## Dashboard Development Overview
This is a simple dashboard implemented using R shiny to enable dog lovers compare different dog breeds in terms of numeric features.

### 1.0 Design process

1. started with 3 mock-up sketches on how the UI/UX will appear and later picked one
2. Started coding the UI. (dropdowns, buttons, textboxes etc)
3. Completed the UI and worked on the server.R codebase to make the UI and back-end sync.
4. Finalized by doing integration tests and temporary hosting

#### **CHECK IT:** <https://dataseniors.shinyapps.io/dogBreeds/>

### 2.0  A subset view of the data used
```{r }
print(head(breed_traits[3:4, c(2:4)]))
```

### 3.0 Packages used 

1. **ggplot2**

2. **reshape2**

3. **dplyr**

### 4.0 Hosting 

The shiny apps can be hosted using AWS EC2 or Digital Ocean droplet.
Alternatively for testing to avoid more costs one can use shinyapps.io


### 5.0 Conclusion 

You can clone the app and run it on your own. 
**Thanks for reading for any query reach out @kochollamikes@gmail.com**