---
title: "One Acre Fund Interview"
author: "Mike Kocholla"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# SMS Impact Analysis on Kenyan Farmers uptake of 1AF program
## Descriptive Analysis

```{r echo=T, comment=F ,warning=FALSE, message=FALSE}
#Read the dataset
kenyan_farmers<-read.csv("~/Documents/GDA_ExerciseData_Sept2019.csv")
head(kenyan_farmers)
names(kenyan_farmers)
nrow(kenyan_farmers)# Total rows in the raw data set
#summary(kenyan_farmers)
```

## Filter out rows for farmers who qualified before Trial
```{r echo=T, comment=F ,warning=FALSE, message=FALSE}
#Need to filter out farmers who qualified before trial.QBT(qualified Before Trials)
library(dplyr)
kenyan_farmers_minus_QBT<-kenyan_farmers%>%filter(QualifiedBeforeTrial==0)
nrow(kenyan_farmers_minus_QBT) # data to be used for impact analysis
```
## Testing the relationship between main treatment and qualification

```{r echo=T, comment=F ,warning=FALSE, message=FALSE}
table1<-table(kenyan_farmers_minus_QBT$Qualified,kenyan_farmers_minus_QBT$MainTreatment)
round(prop.table(table1, 2)*100,2)
```
#### The above results shows that other treatment(sms) performed better than others in qualifying a farmer. To confirm if this is statistically significance further test were carried out.

## Testing for statistical significance
```{r echo=T, comment=F ,warning=FALSE, message=FALSE}
test1<-chisq.test(kenyan_farmers_minus_QBT$Qualified,kenyan_farmers_minus_QBT$MainTreatment)
options(scipen = 999)
test1
```

#### The above statistical test shows that the relatioship between treatments and qualification is significant. We therefore recommend treatments that have 65% chance of qualifying a farmer to be applied together for maximum effect.

# 2. A Logistic Regression Approach - Classification of a farmers likelihood of qualification based on our covariates.

```{r echo=T, comment=F ,warning=FALSE, message=FALSE}
# fit a logistic regression model
mod1<-glm(Qualified~MentionedDeadline+RemainingAmount+LastReminder, data=kenyan_farmers_minus_QBT, family = "binomial")
mod2<-glm(Qualified~MainTreatment, data=kenyan_farmers_minus_QBT, family = "binomial")
summary(mod1)
summary(mod2)
```
#### From model 2 fitting main treatment variables showed accepted p-values for confirming our results from the first method. Best treatment combination here would be T1,T2,T3 and T5. T6 here is not statistically significant hence left out.

#### From model 1 fitting the cross randomized variables showed a non significant result from the p-values. 

